Hydras \& Co.

### 2022-10-11 doc/chapter-fol.tex
start a chapter on FOL

>>>>

\subsection{Formulas}

The type of first order formulas over $L$ is defined 
in~\href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol} as an inductive data type.

\inputsnippets{fol/FormulaDef}

The full abstract syntax of first-order formulas is completed 
with a few more notations. Note that we are studying \emph{classical} first-order logic, so the existential quantifier is derived from the universal one through negation.

\inputsnippets{fol/FolFull, fol/folPlus}

\subsection{Examples}

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.fol_Examples.html}{MoreAck.fol\_Examples}

\inputsnippets{fol_Examples/instantiations}

For instance, the term $v_1+0$ is written as below.

\inputsnippets{fol_Examples/v1Plus01}

Let us give two examples of first-order formulas.

\begin{itemize}
\item $\forall\,v_0\;v_1,\, v_0<v_1\, \longrightarrow\, v_0<v_1 + v_0$
\inputsnippets{fol_Examples/f1Example}
\item $\forall\,v_0,\,\exists\,v_1,\,v_0<v_1$
\inputsnippets{fol_Examples/f2Example}

\end{itemize}

\subsection{Decidability of equality}

Under the assumption that equality is decidable on 
function and relation symbols of any language $L$,
we get decidability of equality on terms and formulas.
Because of dependent types, the proofs are quite long and technical. The reader may consult them in \href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol}

\begin{todo}
  Should we talk about the decomposition lemmas
\texttt{nilTerms} and \texttt{consTerms} ?
\end{todo}

\inputsnippets{fol/formDec1, fol/formDec2,
fol/formDec3,fol/formDec4,fol/formDec5}

\subsection{Induction principles on formula depth}

\subsubsection{Depth of a formula}

\inputsnippets{fol/depthDef}

\inputsnippets{fol_Examples/ltdepth1}

\begin{todo}
Motivate the induction principles based on depth. Compatible with term substitution and universal quantifier elimination.
\end{todo}

\begin{todo}
 Look for the principles which are really used in Ackermann or/and Goedel libraries, and comment them.
 Maybe skip the helpers (unused in other files)
\end{todo}

### 2022-10-11 doc/hydras.tex
start a chapter on FOL

@@

Last but not least, many thanks to Pierrette Cassou-Noguès for the watercolor on page~\pageref{watercolor}.

@@

\part{Ackermann, G\"{o}del, Peano\,\dots}
This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).

@@

\include{chapter-primrec}
\include{chapter-encoding}

>>>>

\newpage
% \mbox{~}
\thispagestyle{empty}
\label{roosterhydra}
 {\centering
      \includegraphics[width=12cm]{rooster-hydra.png}\\
      \centerline{\emph{``The incomplete rooster hydra'': AI art generated by Karl Palmskog}}
}

@@

Last but not least, many thanks to Pierrette Cassou-Noguès for the watercolor on pages~\pageref{watercolorgray} and
\pageref{watercolor}. Thanks to Karl Palmskog for his
\emph{rooster hydra}, page~\pageref{roosterhydra}.

@@

\part{Ackermann, G\"{o}del, Peano\,\dots}
This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

@@

\include{chapter-primrec}
\include{chapter-fol}

\include{chapter-encoding}
